\documentclass[english,xcolor=svgnames]{beamer}


\input{../Latex/teachingslidesbeamer.tex}


\begin{document}

\title{Topics in Macroeconomics }
\vspace{1cm}
\author[shortname]{
\begin{tabular}{cc}
Juan Herre\~{n}o & Johannes Wieland \\ 
\end{tabular}\\
}


\date{UCSD, Spring \the\year}

\setbeamertemplate{footline}{}
\makebeamertitle
\setbeamertemplate{footline}[frame number]{}

\addtocounter{framenumber}{-1}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\AtBeginSection[]{
\setbeamertemplate{footline}{}
  \frame<beamer>{ 

    \frametitle{Outline}   

    \tableofcontents[currentsection,hideallsubsections] 
  }
\setbeamertemplate{footline}[frame number]{}
\addtocounter{framenumber}{-1}
}

\AtBeginSubsection[]{
\setbeamertemplate{footline}{}
  \frame<beamer>{ 

    \frametitle{Outline}   

    \tableofcontents[currentsection,currentsubsection] 
  }
  \setbeamertemplate{footline}[frame number]{}
  \addtocounter{framenumber}{-1}
}



\setbeamertemplate{footline}{}
\begin{frame}
\frametitle{Outline}   
\tableofcontents[hideallsubsections] 
\end{frame}
\addtocounter{framenumber}{-1}
\setbeamertemplate{footline}[frame number]{}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{frame}
\frametitle[alignment=center]{Cross-Sectional Regressions}
\begin{align*}
	Y_i = \alpha_i + \beta X_i + \epsilon_i
\end{align*}
\begin{itemize}
	\item Interested in $\beta$.
	\item Can identify $\beta$ if $E( \epsilon_i|X_i)=0$ or suitable instrument with $E( \epsilon_i|Z_i)=0$.
	\item What's the DGP? Two views:
	\begin{enumerate}
		\item $X_i$ / $Z_i$ is quasi-random heterogenous exposure to the same endogenous shock.
		\item $X_i$ / $Z_i$ is heterogenous, endogenous exposure to heterogenous, quasi-random shocks.
	\end{enumerate}
\end{itemize}
\end{frame}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Goldsmith-Pinkham, Sorkin, and Swift, AER 2020}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}
\frametitle[alignment=center]{Bartik: Canonical Example}
\begin{itemize}
	\item Structural equation:
	\begin{align*}
		y_l = \tau +\beta x_l + \epsilon_l
	\end{align*}
	\begin{itemize}
		\item $y_l$: wage growth in area $l$.
		\item $x_l$: employment growth in area $l$.
	\end{itemize}
	\item Identities:
	\begin{align*}
		x_l = \sum_k z_{l,k} g_{l,k}, \qquad\qquad g_{l,k} = g_k + \tilde{g}_{l,k}
	\end{align*}
	\begin{itemize}
		\item $z_{l,k}$: employment share in area $l$ in industry $k$.
		\item $g_{l,k}$: employment growth in area $l$ in industry $k$.
		\item $g_{k}$: national employment growth in industry $k$.
		\item $\tilde{g}_{l,k}$:  idiosyncratic component of employment growth rate.
	\end{itemize}
	\item Bartik (1991) instrument to estimate inverse labor supply elasticity:
	\begin{align*}
		B_l = \sum_k z_{l,k}g_k
	\end{align*}
	\item What is exogenous? Shares? Shocks? Product?
\end{itemize}
\end{frame}

\begin{frame}
\frametitle[alignment=center]{General Setup}
\begin{itemize}
	\item x
\end{itemize}
\end{frame}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Borusyak, Hull, and Jaravel, RESTUD 2022}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Nakamura and Steinsson, AER 2014}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Mian, Rao, and Sufi, QJE 2013}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\end{document}